A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Finish Conclusions.
Revise Description on meta variables

\red{, which is called a \textit{stage variable} in \LMD.}
\red{ which is called a stage in \LMD.}
\red{Although we can apply any transition to a transition abstraction in \LTP,
we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G))                         \\
\end{align*}

The metavariables $X, Y, \text{and} Z$ range over the type variables, $c$ ranges over constants, the metavariables $x, y, \text{and}, z$ range over the variables.
The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
$\epsilon$ is a symbol for an empty transition.

@@

In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
$\Lambda\alpha.M$ is a stage variable abstraction.
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
$\%_\alpha M$ is a primitive operator for cross-stage persistence.

@@

>>>>

\red{以下の3文をどこかに入れる必要がある}
\red{, which is called a \textit{stage variable} in \LMD.}
\red{ which is called a stage in \LMD.}
\red{Although we can apply any transition to a transition abstraction in \LTP,
we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
	                         &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M         \\  
	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                               \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G))               \\
\end{align*}

% Description on meta variables

The metavariables $X, Y$, and $Z$ range over the type variables.
$x, y$, and, $z$ range over the variables.
The metavariables $\alpha, \beta, \text{and} \gamma$ range over the transition variables.
A transition, denoted by $A$ and $B$, is a finite sequence of transition variables.
$\epsilon$ is a symbol for the empty transition.

@@

\red{ 
$c$ ranges over constants, 
}
In addition to normal terms in Simply Typed Lambda Calculus, there are five more forms.
$\TB_\alpha M$ represents a code fragment, and $\TB_\alpha M$ represents unquote.
$\Lambda\alpha.M$ is a stage variable abstraction.
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable.
$\%_\alpha M$ is a primitive operator for cross-stage persistence.

@@

Making algorithmic typing and equality rules for \LMD is a future work.
They would be complicated but possible 
because we can realize them by defining a new weak head normal form which contains $\%$ erasing rule.
